Dynamic Knapsack Problem

### 2021-07-06 v2-Manuscript/Manuscript.tex
testing version 2

\subsection{State Space}
\subsubsection{Description}
State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1
    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

@@

	\item Define Resource Violation Variable
	\begin{alignat}{10}
			& \hat{uv}_{tp} 
				&& \le  M(uvb_{tp}) \quad
				&& \forall tp \\
			& \hat{uv}_{1p} 
				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
				&& \forall p \\
			& \hat{uv}_{tp} 
				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
				&& \forall t \in \{ 2..T \} p \\
	\end{alignat}

	\item Define Units Left Over Variable
	\begin{alignat}{10}
			& \hat{ul}_{p} 
				&& \ge 0 \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \le M (ulb_{p}) \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
				&& \forall p
	\end{alignat}
\end{itemize}

@@

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
	\begin{alignat}{10}
		& ul'_{p} 
			&& = \hat{ul}_{p} + ued_{p} \quad 
			&& \forall p
	\end{alignat}

@@

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&	+
				\overbrace{
					\sum_{tmdc} cs^{t} (sc_{tmdc})
				}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				(1.5cc) \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				(0.5cc) \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation*}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
\end{equation*}

>>>>

\subsection{State Space}
\subsubsection{Description}
State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1. This is only for resources that can be carried over
    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

@@

	\item Define Resource Violation Variable
	\begin{alignat}{10}
			& \hat{uv}_{tp} 
				&& \le  M(uvb_{tp}) \quad
				&& \forall tp \\
			& \hat{uv}_{1p} 
				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
				&& \forall p \in \{\text{Carry Over}\} \\
			& \hat{uv}_{1p} 
				&& \le  (\hat{uu}_{1p} - uen_{1p}) + M(1-uvb_{tp}) \quad
				&& \forall p \in \{\text{Non Carry Over}\} \\
			& \hat{uv}_{tp} 
				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
				&& \forall t \in \{ 2..T \} p \\
	\end{alignat}

	\item Define Units Left Over Variable
	\begin{alignat}{10}
			& \hat{ul}_{p} 
				&& \ge 0 \quad 
				&& \forall p \in \{\text{Non Carry Over}\} \\
			& \hat{ul}_{p} 
				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
				&& \forall p \in \{\text{Non Carry Over}\} \\
			& \hat{ul}_{p} 
				&& \le M (ulb_{p}) \quad 
				&& \forall p \in \{\text{Non Carry Over}\} \\
			& \hat{ul}_{p} 
				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
				&& \forall p \in \{\text{Non Carry Over}\}
	\end{alignat}
\end{itemize}

@@

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
	\begin{alignat}{10}
		& ul'_{p} 
			&& = \hat{ul}_{p} + ued_{p} \quad 
			&& \forall p \in \{ \text{Carry Over}\} \\
	\end{alignat}

@@

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m+1} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tmdc} cw^{M+1} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&	+
				\overbrace{
					\sum_{tmdc} cs^{t} (sc_{tmdc})
				}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				(1.5cc) \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				(0.5cc) \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation*}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) + \gamma v(S')
\end{equation*}
